Place of death in NRS COVID-19 deaths: visualisation for 2024 data

### 2024-02-07 covid_nrs_place_of_death_visualisations_2024.Rmd
refactored adding vline and annotate to graphs over time to automatically infer from current year of data how many to add

fig_place_of_death <-
  merged_deaths_overall %>%
  filter(sex == "all" & age == "all") %>%
  filter(!place_of_death %in% c("All","Other")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2021), linetype = "dashed", colour="grey50") +  # start of 2021
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2022), linetype = "dashed", colour="grey50") +  # start of 2022
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2023), linetype = "dashed", colour="grey50") +  # start of 2023
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2024), linetype = "dashed", colour="grey50") +  # start of 2024
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,removed_other_category_text,source_nrs_text), collapse="\n"),
       colour = "Cause of death"
       ) +
  ## annotate historic range
  geom_text(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="text"), aes(x=x, y=y, label=label),  colour = "grey20", size = 8 / (14/5)) +  # the size is tricky
  geom_curve(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="curve"), aes(x=x, y=y, xend=xend, yend=yend), colour = c("#4477aa", "grey20"), alpha = c(0.5, 1), curvature = 0.20, arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom = "text", x=ymd("2021-01-07"), y=30, label = "'21", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2022-01-07"), y=30, label = "'22", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2023-01-02"), y=30, label = "'23", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2024-01-01"), y=30, label = "'24", hjust = 0, colour = "grey40") +
  NULL

@@

fig_place_of_death_2015_2019_range <-
  merged_deaths_overall_2015_2019_historic_period %>%
  filter(sex == "all" & age == "all") %>%
  filter(!place_of_death %in% c("All","Other")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2021), linetype = "dashed", colour="grey50") +  # start of 2021
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2022), linetype = "dashed", colour="grey50") +  # start of 2022
   geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2023), linetype = "dashed", colour="grey50") +  # start of 2023
   geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2024), linetype = "dashed", colour="grey50") +  # start of 2024
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,historic_period_2015_2019_text,source_nrs_text), collapse="\n"),
       colour = "Cause of death"
       ) +
  ## annotate historic range
  geom_text(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="text"), aes(x=x, y=y, label=label),  colour = "grey20", size = 8 / (14/5)) +  # the size is tricky
  geom_curve(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="curve"), aes(x=x, y=y, xend=xend, yend=yend), colour = c("#4477aa", "grey20"), alpha = c(0.5, 1), curvature = 0.20, arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom = "text", x=ymd("2021-01-07"), y=30, label = "'21", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2022-01-07"), y=30, label = "'22", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2023-01-02"), y=30, label = "'23", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2024-01-01"), y=30, label = "'24", hjust = 0, colour = "grey40") +
  NULL

@@

```{r}
fig_place_of_death_home_only <-
  merged_deaths_overall %>%
  filter(sex == "all" & age == "all") %>%
  filter(place_of_death %in% c("Home & other non-institution")) %>%  # home death only
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2021), linetype = "dashed", colour="grey50") +  # start of 2021
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2022), linetype = "dashed", colour="grey50") +  # start of 2022
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2023), linetype = "dashed", colour="grey50") +  # start of 2023
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2024), linetype = "dashed", colour="grey50") +  # start of 2024
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,historic_period_2022_text,source_nrs_text), collapse="\n")
       ) +
  ## annotate historic range
  annotate(geom="text",x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 50, label = "Historic range (min & max)", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 29, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 33, year_number = 2020), y = 65, yend = 210, curvature = 0.20, colour = "#4477aa", alpha = 0.5, arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom="text", x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 100, label = "Historic mean", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 22, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 25, year_number = 2020), y = 115, yend = 270, curvature = 0.20, colour = "grey20", linetype="dashed", arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom = "text", x=ymd("2021-01-07"), y=30, label = "'21", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2022-01-07"), y=30, label = "'22", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2023-01-02"), y=30, label = "'23", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2024-01-01"), y=30, label = "'24", hjust = 0, colour = "grey40") +
  NULL

@@

```{r}
fig_place_of_death_home_2015_2019_historic_period <-
  merged_deaths_overall_2015_2019_historic_period %>%
  filter(sex == "all" & age == "all") %>%
  filter(place_of_death %in% c("Home & other non-institution")) %>%  # home death only
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2021), linetype = "dashed", colour="grey50") +  # start of 2021
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2022), linetype = "dashed", colour="grey50") +  # start of 2022
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2023), linetype = "dashed", colour="grey50") +  # start of 2023
  geom_vline(xintercept = compute_start_date_from_week_number(week_number = 1, year_number = 2024), linetype = "dashed", colour="grey50") +  # start of 2024
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,historic_period_2015_2019_text,source_nrs_text), collapse="\n")
       ) +
  ## annotate historic range
  annotate(geom="text",x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 50, label = "Historic range (min & max)", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 29, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 33, year_number = 2020), y = 65, yend = 210, curvature = 0.20, colour = "#4477aa", alpha = 0.5, arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom="text", x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 100, label = "Historic mean", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 22, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 25, year_number = 2020), y = 115, yend = 270, curvature = 0.20, colour = "grey20", linetype="dashed", arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom = "text", x=ymd("2021-01-07"), y=30, label = "'21", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2022-01-07"), y=30, label = "'22", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2023-01-02"), y=30, label = "'23", hjust = 0, colour = "grey40") +
  annotate(geom = "text", x=ymd("2024-01-01"), y=30, label = "'24", hjust = 0, colour = "grey40") +
  NULL

>>>>

fig_place_of_death <-
  merged_deaths_overall %>%
  filter(sex == "all" & age == "all") %>%
  filter(!place_of_death %in% c("All","Other")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  add_vertical_lines_for_start_of_year(years = 2021:current_year) +
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       # caption = paste0(c(death_registrations_text,removed_other_category_text,source_nrs_text), collapse="\n"),
       colour = "Cause of death"
       ) +
  ## annotate historic range
  geom_text(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="text"), aes(x=x, y=y, label=label),  colour = "grey20", size = 8 / (14/5)) +  # the size is tricky
  geom_curve(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="curve"), aes(x=x, y=y, xend=xend, yend=yend), colour = c("#4477aa", "grey20"), alpha = c(0.5, 1), curvature = 0.20, arrow = arrow(length = unit(0.2, "cm"))) +
  add_annotations_for_start_of_year(years = 2021:current_year) +
  NULL

@@

fig_place_of_death_2015_2019_range <-
  merged_deaths_overall_2015_2019_historic_period %>%
  filter(sex == "all" & age == "all") %>%
  filter(!place_of_death %in% c("All","Other")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  add_vertical_lines_for_start_of_year(years = 2021:current_year) +
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,historic_period_2015_2019_text,source_nrs_text), collapse="\n"),
       colour = "Cause of death"
       ) +
  ## annotate historic range
  geom_text(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="text"), aes(x=x, y=y, label=label),  colour = "grey20", size = 8 / (14/5)) +  # the size is tricky
  geom_curve(data = annotations_fig_place_of_death_explaining_historic_range %>% filter(geom=="curve"), aes(x=x, y=y, xend=xend, yend=yend), colour = c("#4477aa", "grey20"), alpha = c(0.5, 1), curvature = 0.20, arrow = arrow(length = unit(0.2, "cm"))) +
  add_annotations_for_start_of_year(years = 2021:current_year) +
  NULL

@@

```{r}
fig_place_of_death_home_only <-
  merged_deaths_overall %>%
  filter(sex == "all" & age == "all") %>%
  filter(place_of_death %in% c("Home & other non-institution")) %>%  # home death only
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  add_vertical_lines_for_start_of_year(years = 2021:current_year) +
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,historic_period_2022_text,source_nrs_text), collapse="\n")
       ) +
  ## annotate historic range
  annotate(geom="text",x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 50, label = "Historic range (min & max)", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 29, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 33, year_number = 2020), y = 65, yend = 210, curvature = 0.20, colour = "#4477aa", alpha = 0.5, arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom="text", x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 100, label = "Historic mean", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 22, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 25, year_number = 2020), y = 115, yend = 270, curvature = 0.20, colour = "grey20", linetype="dashed", arrow = arrow(length = unit(0.2, "cm"))) +
  add_annotations_for_start_of_year(years = 2021:current_year) +
  NULL

@@

```{r}
fig_place_of_death_home_2015_2019_historic_period <-
  merged_deaths_overall_2015_2019_historic_period %>%
  filter(sex == "all" & age == "all") %>%
  filter(place_of_death %in% c("Home & other non-institution")) %>%  # home death only
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  pivot_longer(cols = c(deaths_all_causes, deaths_non_covid), 
               names_to = "deaths_type", values_to = "deaths") %>% 
  ggplot(aes(x = date_w_c)) +
  add_vertical_lines_for_start_of_year(years = 2021:current_year) +
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "12 weeks", limits = c(earliest_date, most_recent_date_available_2024)) +
  geom_ribbon(aes(ymin = deaths_min, ymax = deaths_max), fill = "#4477aa", alpha = 0.5) +
  geom_line(aes(y = deaths, colour = deaths_type)) +
  geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_grid(~place_of_death) +
  scale_colour_manual(values = c("red","blue"),  # custom legend for the two lines
                      labels = c("All deaths", 
                                 "Non Covid-19 deaths"),
                      guide = guide_legend(label.hjust = 0.5, override.aes = list(size = 5))
                      ) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = NULL,
       y = "Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c(death_registrations_text,historic_period_2015_2019_text,source_nrs_text), collapse="\n")
       ) +
  ## annotate historic range
  annotate(geom="text",x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 50, label = "Historic range (min & max)", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 29, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 33, year_number = 2020), y = 65, yend = 210, curvature = 0.20, colour = "#4477aa", alpha = 0.5, arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom="text", x = compute_start_date_from_week_number(week_number = 20, year_number = 2020), y = 100, label = "Historic mean", colour = "grey20") +
  annotate(geom="curve",x = compute_start_date_from_week_number(week_number = 22, year_number = 2020), xend = compute_start_date_from_week_number(week_number = 25, year_number = 2020), y = 115, yend = 270, curvature = 0.20, colour = "grey20", linetype="dashed", arrow = arrow(length = unit(0.2, "cm"))) +
  add_annotations_for_start_of_year(years = 2021:current_year) +
  NULL
